Mining Interaction Log Data in a Creative Arts Practice using Transition Matrices

### 2015-09-23 flux-entropy-paper/flux-entropy-paper.tex
yes, it's still the median

Some of these session contexts are are shown
Figure~\ref{fig:three-performance-contexts} and other descriptive
statistics about the corpus are shown in Table \ref{corpus-table}.
In our corpus, the median length of sessions is 7m26s (IS THIS STILL THE MEDIAN IGNORING THE
DEMONSTRATION AND DATA GATHERING SESSIONS?) and the median
number of participants per ensemble is four. Each session record is
labelled with metadata about its \emph{context} (concert,
rehearsal, recording), its \emph{type} (improvisation or composition),
and its \emph{instrumentation} (iPads-only, or iPads with acoustic
percussion). The distribution of recorded sessions by context and type
is shown in Figure \ref{fig:count-data}.

>>>>

Some of these session contexts are are shown
Figure~\ref{fig:three-performance-contexts} and other descriptive
statistics about the corpus are shown in Table \ref{corpus-table}.
In our corpus, the median length of sessions is 7m26s and the median
number of participants per ensemble is four. Each session record is
labelled with metadata about its \emph{context} (concert,
rehearsal, recording), its \emph{type} (improvisation or composition),
and its \emph{instrumentation} (iPads-only, or iPads with acoustic
percussion). The distribution of recorded sessions by context and type
is shown in Figure \ref{fig:count-data}.
